%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Qingyuan Wu} \\ \vspace{1pt}
    University of Southampton, Southampton, SO14 3LG \\ \vspace{1pt}
    \small 
    % \raisebox{-0.1\height}\faPhone\ +44 07827197603 
    ~ \href{mailto:qingyuanwu4work@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mail}} 
    ~ \href{https://qingyuanwunothing.github.io/}{\raisebox{-0.2\height}\faHome\  \underline{homepage}} 
    ~ \href{https://linkedin.com/in/qingyuan-wu-441412290/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin}}  ~
    \href{https://github.com/QingyuanWuNothing}{\raisebox{-0.2\height}\faGithub\ \underline{github}}
    \vspace{-8pt}
\end{center}


%------RESEARCH INTEREST-------
\section{Research Interests}
  \resumeSubHeadingListStart
    \resumeSubheading{Reinforcement Learning, Machine Learning}{}
      {}{}
  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southampton}{Sep. 2024 -- Sep. 2026 (Expected)}
      {Doctorate of Philosophy in Computer Science}{Southampton, UK}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Liverpool}{Sep. 2023 -- Sep. 2024}
      {Doctorate of Philosophy in Computer Science (transfer to Southampton)}{Liverpool, UK}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanjing University of Aeronautics and Astronautics}{Sep. 2019 -- April 2022}
      {Master of Engineering in Computer Science}{Nanjing, CN}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanjing University of Aeronautics and Astronautics}{Sep. 2015 -- June 2019}
      {Bachelor of Science in Mathematics}{Nanjing, CN}
  \resumeSubHeadingListEnd

%------WORK EXPERIENCE-------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Parametrix.AI Technology}{April 2022 -- Sep. 2023}
      {Reinforcement Learning and Gaming AI Researcher, full time}{ShenZhen, CN}
      \resumeItemListStart
            \resumeItem{Working on the most challenging and complicated gaming scenarios(e.g., FPS, TPS).}
            \resumeItem{Developed various and lively gaming AI (e.g., human-like, highly-skilled).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeSubHeadingListStart
      % \resumeProjectHeading
      %     {\textbf{Under Review}\emph{}}{}
      %     \resumeItemListStart
      %       \resumeItem{}
      %     \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Conference}\emph{}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Qingyuan Wu}, Simon Sinong Zhan, Yixuan Wang, Yuhui Wang, Chung-Wei Lin, Chen Lv, Qi Zhu, Chao Huang. \textit{Variational Delayed Policy Optimization.} Conference on Neural Information Processing Systems 2024 (NeurIPS 2024).}
            \resumeItem{\textbf{Qingyuan Wu}, Simon Sinong Zhan, Yixuan Wang, Yuhui Wang, Chung-Wei Lin, Chen Lv, Qi Zhu, Jürgen Schmidhuber, Chao Huang. \textit{Boosting Reinforcement Learning with Strongly Delayed Feedback Through Auxiliary Short Delays.} International Conference on Machine Learning 2024 (ICML 2024).}
            \resumeItem{Yuhui Wang, Weida Li, Francesco Faccio,\textbf{Qingyuan Wu}, Jürgen Schmidhuber. \textit{Highway Value Iteration Networks.} International Conference on Machine Learning 2024 (ICML 2024).}
            \resumeItem{Simon Sinong Zhan, Yixuan Wang, \textbf{Qingyuan Wu}, Ruochen Jiao, Chao Huang, Qi Zhu. \textit{State-wise Safe Reinforcement Learning With Pixel Observations.} Learning for Dynamics \& Control Conference 2024 (L4DC 2024).}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Journal}\emph{}}{}
          \resumeItemListStart
            \resumeItem{Dan Zhu, Xiaohong Chen, \textbf{Qingyuan Wu}, Shunming Li. \textit{Subspace Clustering Induced by Adaptive Graph Learning}. Computer Engineering and Applications, 56(21):8, 2019.}
            % \resumeItem{}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Thesis}\emph{}}{}
          \resumeItemListStart
            \resumeItem{[Master thesis] \textit{Research on Efficient Exploration and Learning Method Based on Rollout in Complex Scenarios.} Advised by Prof. Xiaoyang Tan}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Preprint}\emph{}}{}
          \resumeItemListStart
            \resumeItem{Simon Sinong Zhan, \textbf{Qingyuan Wu},  Zhian Ruan, Frank Yang, Philip Wang, Yixuan Wang, Ruochen Jiao, Chao Huang, Qi Zhu. \textit{Inverse Delayed Reinforcement Learning.} arxiv: 2412.02931.}
            \resumeItem{Simon Sinong Zhan, \textbf{Qingyuan Wu},  Philip Wang, Yixuan Wang, Ruochen Jiao, Chao Huang, Qi Zhu. \textit{Model-based Reward Shaping for Adversial Inverse Reinforcement Learning in Stochastic Environments.} arxiv: 2410.03847.}
            \resumeItem{Yuhui Wang, \textbf{Qingyuan Wu}, Weida Li, Dylan R. Ashley, Francesco Faccio, Chao Huang, Jürgen Schmidhuber. \textit{Scaling Value Iteration Networks to 5000 Layers for Extreme Long-Term Planning.} arxiv: 2406.08404v1.}
            \resumeItem{Yuhui Wang, Miroslav Strupl, Francesco Faccio, \textbf{Qingyuan Wu}, Haozhe Liu, Michał Grudzień, Xiaoyang Tan, Jürgen Schmidhuber. \textit{Highway Reinforcement Learning.} arxiv: 2405.18289.}
            \resumeItem{Jiayu Yao, \textbf{Qingyuan Wu}, Quan Feng, Songcan Chen. \textit{Learning downstream task by selectively capturing complementary knowledge from multiple self-supervisedly learning pretexts.} arxiv: 2204.05248, 2022.}
            \resumeItem{\textbf{Qingyuan Wu}, Yuhui Wang. \textit{Expected-Max Ensembled Q-learning with Temporally-Varying Exploration.} 2021.}
            \resumeItem{Yuhui Wang, \textbf{Qingyuan Wu}, Pengcheng He, Xiaoyang Tan. \textit{A Novel Greedy-Step Bellman Optimality Equation for Efficient Value Propagation.} arxiv: 2102.11717, 2021.}
            \resumeItem{\textbf{Qingyuan Wu}, Xiaoyang Tan. \textit{Graph-Constrained Monte Carlo Tree Search for Low Variance Bus Driver Scheduling.} 2021.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{}\emph{}}{}
%           \resumeItemListStart
%             \resumeItem{}
%             \resumeItem{}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Skills}{: Python, C++, Pytorch, Tensorflow} \\
    }}
 \end{itemize}

 
% %-----------HONOURS And REWARDS-----------
% \section{Honours and Rewards}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{
%     \item{\textbf{Honours}{: }}
%     \item{\textbf{Rewards}{: }}
%     }
%  \end{itemize}
 
 \vspace{-16pt}

\end{document}
